Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2014-12-22 Paper/paper.tex
Have updated proof and tweaked intro

@@

Patients in CCUs need constant medical support to keep their body functioning.
Many previous researchers have developed queueing models to help manage bed capacities in hospitals \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
Also, a vast amount of literature has been devoted to the simulation of CCUs;  \cite{Cahill1999a,Costa2003,Griffiths2004a,Kim1999,Litvak2008,Shahani2008}.

@@

The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

@@

The aim of this paper is to further investigate the effect of rational policies employed by Hospitals.
In particular, the aim is to place this in a game theoretic setting so as to identify whether or not target policies result in uncoordinated behaviour that is damaging for patients.

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,8}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\RG}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at RG};
                % lambda
                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KRG
                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
\end{figure}

Based on the previous observation this in turn implies:

\begin{equation}
    U_{\NH}(K_{\RG}) = U_{\NH}(\bar \lambda_{\RG}(K_{\RG}) \geq U_{\NH}(\bar \lambda_{\RG}(K_{\RG}+1)) = U_{\NH}(K_{\RG}+1)
    \label{equ:UNH_as_a_function_of_KRG}
\end{equation}

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives:

\begin{equation}
    U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)
    \label{equ:UNH_as_a_function_of_KNH}
\end{equation}

@@

            % Horizontal inequalities
            \foreach \x in {1.5,2.5,3.5,4.5,5.5}
                {
                \foreach \y in {1,2,3,4,5}
                    {
                        \node at (\x, \y) [red!100] {\textbf{\(\leq\)}};
                    };
                };
        \end{tikzpicture}
    \end{center}
    \caption{Values \(U_{\NH}\).}\label{fig:variation_of_UNH}
\end{figure}

As \(U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
Let \(f^+(K_{\RG})=\argmin_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\geq t\}}(U_{\NH}(k, K_{\RG}))\) and \(f^-(K_{\RG})=\argmax_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\leq t\}}(U_{\NH}(k, K_{\RG}))\).
So that \(f^{\pm}({K_{\RG}})\) is the value of \(K_{\NH}\) that gives the value of \(U_{\NH}(K_{\NH}, K_{\RG})\) that is closest to \(t\) such that:

@@

\begin{equation}
S(K_{\RG}) = \{f^{+}(K_{\RG})\}\cup\{f^{-}(K_{\RG})\}
\end{equation}

Thus, \(f(K_{\RG})\in S(K_{\RG})\).
Note that from (\ref{equ:UNH_as_a_function_of_KNH}) have \(\max S(K_{\RG})=f^{+}(K_{\RG})\) and \(\min S(K_{\RG})=f^{+}(K_{\RG})\).
In essence \(S(K_{\RG})\) corresponds to the set of two values of \(K_{\NH}\) that give a utilisation just below and just above \(t\).

@@

\begin{enumerate}
    \item \(S(K_{\RG})\ne S(K_{\RG})\)
    \item \(S(K_{\RG})= S(K_{\RG})\)
\end{enumerate}

If \(S(K_{\RG})\ne S(K_{\RG})\) this implies that \(f^{+}(K_{\RG})\leq f^{-}(K_{\RG})\) which gives:

@@

To finish the proof consider \(S(K_{\RG})= S(K_{\RG})\) and assume:

\begin{equation}
    f(K_{RG})=f^{+}(K_{\RG}) \text{ but } f(K_{RG}+1)=f^{-}(K_{\RG}+1)
\end{equation}

which contradicts the required result.

@@

\[a^{\pm}=(f^{\pm}(K_{\RG}), K{\RG})\text{ and }b^{\pm}=(f^{\pm}(K_{\RG}+1), K{\RG}+1)\]

@@

this implies:

>>>>

The aim of this paper is to further investigate the effect of rational policies employed by Hospitals.
In particular, the goal is to place this in a game theoretic setting so as to identify whether or not target policies result in uncoordinated behaviour that is damaging for patients.

@@

Many previous researchers have developed queueing models to help manage bed capacities in hospitals \cite{Cooper1974,Dumas1984,Gallivan2011,Gorunescu2002a,Griffiths2012,Harper2002a}.
Also, a vast amount of literature has been devoted to the simulation of CCUs;  \cite{Cahill1999a,Costa2003,Griffiths2004a,Kim1999,Litvak2008,Shahani2008}.

@@

The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{williams2015mathematical}.
This state dependent model was applied to both NH and RG separately.
It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.

@@

@@

\begin{figure}[!hbtp]
    \begin{center}
        \begin{tikzpicture}[scale=.8, every node/.style={scale=0.8}]
            \foreach \x in {0,9}
            {\coordinate (origin) at (\x,0);
                % Coordinate system
                \draw [very thick, ->] (origin) -- ($(origin) + (0,5)$) node[anchor=south east] {\(\bar\lambda_{K_{\RG}}\)};
                \draw [very thick, ->] (origin) -- ($(origin) + (5,0)$) node[anchor=west] {Occupancy at RG};
                % lambda
                \draw ($(origin) + (0,2)$) -- ($(origin) + (2,2)$) -- ($(origin) + (2,4)$) -- ($(origin) + (5,4)$);
                \node at ($(origin) + (1,2.5)$) {\(\lambda_{\NH}^{(l,l)}\)};
                \node at ($(origin) + (3.5,4.5)$) {\(\lambda_{\NH}^{(l,h)}\)};
                % Effect of KRG
                \draw [dashed] ($(origin) + (0,2)$) -- ($(origin) + (4,2)$) -- ($(origin) + (4,4)$);
                \draw [dashed] ($(origin) + (2,0)$) -- ($(origin) + (2,2)$);
                \draw [dashed] ($(origin) + (4,0)$) -- ($(origin) + (4,2)$);
                \draw [very thick, ->] ($(origin) + (2.5,3)$) -- ($(origin) + (3.5,3)$);
                \node at ($(origin) + (2,0)$) [below] {\(K_{\RG}\)};
                \node at ($(origin) + (4,0)$) [below] {\(K_{\RG}+1\)};
            };
        \end{tikzpicture}
    \end{center}
    \caption{The effect of \(K_{\RG}\) on \(\bar \lambda\).}\label{fig:effect_of_KRG_on_arrival_rate}
\end{figure}

Based on the previous observation this in turn implies: \(U_{\NH}(K_{\RG}) = U_{\NH}(\bar \lambda_{\RG}(K_{\RG}) \geq U_{\NH}(\bar \lambda_{\RG}(K_{\RG}+1)) = U_{\NH}(K_{\RG}+1)\) giving:

\begin{equation}
    U_{\NH}(K_{\RG}) \geq U_{\NH}(K_{\RG}+1)
    \label{equ:UNH_as_a_function_of_KRG}
\end{equation}

In the same way (illustrated by Figure \ref{fig:effect_of_KNH_on_arrival_rate}), this gives: \(U_{\NH}(K_{\NH}) = U_{\NH}(\bar \lambda_{\NH}(K_{\NH}) \leq U_{\NH}(\bar \lambda_{\NH}(K_{\NH}+1)) = U_{\NH}(K_{\NH}+1)\) giving:

\begin{equation}
    U_{\NH}(K_{\NH}) \leq U_{\NH}(K_{\NH}+1)
    \label{equ:UNH_as_a_function_of_KNH}
\end{equation}

@@

            % Horizontal inequalities
            \foreach \x in {1.5,2.5,3.5,4.5,5.5}
                {
                \foreach \y in {1,2,3,4,5}
                    {
                        \node at (\x, \y) [red!100] {\textbf{\(\leq\)}};
                    };
                };
        \end{tikzpicture}
    \end{center}
    \caption{Values of \(U_{\NH}\) and the corresponding inequalities for varying cutoff thresholds.}\label{fig:variation_of_UNH}
\end{figure}

As \(U_{\NH}\) increases from the lowest value (top left in Figure  \ref{fig:variation_of_UNH}) to the highest (bottom right in Figure \ref{fig:variation_of_UNH}) the value of \(U_{\NH}-t\) will change sign (from negative to positive).
Let:

\begin{equation}
f^+(K_{\RG})=\argmin_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\geq t\}}(U_{\NH}(k, K_{\RG}))
\end{equation}
 and

\begin{equation}
f^-(K_{\RG})=\argmax_{\{0\leq k \leq C_{\NH}|U_{\NH}(k, K_{\RG})\leq t\}}(U_{\NH}(k, K_{\RG}))
\end{equation}

Thus, \(f^{\pm}({K_{\RG}})\) is the value of \(K_{\NH}\) that gives the value of \(U_{\NH}(K_{\NH}, K_{\RG})\) that is closest to \(t\) such that:

@@

\begin{equation}
S(K_{\RG}) = \{f^{-}(K_{\RG})\}\cup\{f^{+}(K_{\RG})\}
\end{equation}

Thus, \(f(K_{\RG})\in S(K_{\RG})\).
Note that from (\ref{equ:UNH_as_a_function_of_KNH}) \(\max (S(K_{\RG}))=f^{+}(K_{\RG})\) and \(\min S(K_{\RG})=f^{+}(K_{\RG})\).
In essence \(S(K_{\RG})\) corresponds to the set of two values of \(K_{\NH}\) that give a utilisation just below and just above \(t\).

@@

\begin{enumerate}
    \item \(S(K_{\RG})\ne S(K_{\RG}+1)\)
    \item \(S(K_{\RG})= S(K_{\RG}+1)\)
\end{enumerate}

If \(S(K_{\RG})\ne S(K_{\RG})\) this implies that \(f^{+}(K_{\RG})\leq f^{-}(K_{\RG}+1)\) which gives:

@@

To finish the proof consider \(S(K_{\RG})=S(K_{\RG})\) which is equivalent to \(f^{\pm}(K_{\RG})=f^{\pm}(K_{\RG}+1)\) and assume:

\begin{equation}
    f(K_{\RG})=f^{+}(K_{\RG}) \text{ but } f(K_{\RG}+1)=f^{-}(K_{\RG}+1)
\end{equation}

which, because it has been assumed that \(f^{-}(K_{\RG}+1)=f^{-}(K_{\RG})\), contradicts the required result (as this would imply that \(f(K_{\RG})< f(K_{\RG}+1)\).

@@

\[a^{\pm}=(f^{\pm}(K_{\RG}), K_{\RG})\text{ and }b^{\pm}=(f^{\pm}(K_{\RG}+1), K_{\RG}+1))=(f^{\pm}(K_{\RG}), K_{\RG}+1))\]

@@
